---
title: "Multilinear Regression"
author: "Jonathan Then"
date: '2022-10-22'
output: html_document
---

```{r setup, warning=FALSE}
#LIBRARIES
library(tidyverse)
library(sjPlot)
library(caret)
```

UNDERSTANDING THE DATA
ndvi_se – Pixel southeast of city centroid
ndvi_sw – Pixel southwest of city centroid
ndvi_ne – Pixel northeast of city centroid
ndvi_nw – Pixel northwest of city centroid

precipitation_amt_mm – Total precipitation

reanalysis_air_temp_k – Mean air temperature
reanalysis_precip_amt_kg_per_m2 – Total precipitation
reanalysis_relative_humidity_percent – Mean relative humidity
reanalysis_tdtr_k – Diurnal temperature range

station_avg_temp_c – Average temperature
station_diur_temp_rng_c – Diurnal temperature range
station_max_temp_c – Maximum temperature
station_min_temp_c – Minimum temperature
station_precip_mm – Total precipitation


```{r}
#READ IN DATA
data_features = read.csv('dengue_features_train.csv')
data_labels = read.csv('dengue_labels_train.csv')

#REMOVE week_start_date
data_features = subset(data_features, select = -c(week_start_date))

#REMOVE index columns and correlated columns
data_features = subset(data_features, select = -c(reanalysis_avg_temp_k, reanalysis_dew_point_temp_k, reanalysis_max_air_temp_k, reanalysis_min_air_temp_k, reanalysis_sat_precip_amt_mm, reanalysis_specific_humidity_g_per_kg))

#REPLACE NA
data_features[is.na(data_features)] <- 0

#GROUP by city
sj <- data_features %>% filter(city == "sj")
iq <- data_features %>% filter(city == "iq")

#JOIN predictor into dataset
sj_cases <- subset(data_labels, city =="sj", select = total_cases)
iq_cases <- subset(data_labels, city =="iq", select = total_cases)

sj <- cbind(sj, sj_cases)
iq <- cbind(iq, iq_cases)

#REMOVE index columns
sj = subset(sj, select = -c(city, year, weekofyear))
iq = subset(iq, select = -c(city, year, weekofyear))
```

```{r}
#Multilinear Regression Model Full Model - San Juan
M0 = lm(total_cases ~ 1, data = sj)
M1 = lm(total_cases ~ ., data = sj)

sjPlot::tab_model(M1, digits = 4, show.ci = FALSE)
```

```{r}
#Backward Stepwise Search using AIC (SJ)
step.back.aic = step(M1, direction = "backward",trace = FALSE)
summary(step.back.aic)
```

```{r}
#Forward Stepwise Search using AIC (SJ)
step.fwd.aic = step(M0, scope = list(lower = M0, upper = M1), direction = "forward", trace = FALSE)
summary(step.fwd.aic)
```

```{r}
sjPlot::tab_model(
step.fwd.aic, step.back.aic,
show.ci = FALSE,
show.aic = TRUE,
dv.labels = c("Forward model (SJ)","Backward model (SJ)")
)
```

```{r}
#Multilinear Regression Model Full Model - Iquitos
M2 = lm(total_cases ~ 1, data = iq)
M3 = lm(total_cases ~ ., data = iq)

sjPlot::tab_model(M3, digits = 4, show.ci = FALSE)
```

```{r}
#Backward Stepwise Search using AIC (IQ)
step.back.aic = step(M3, direction = "backward",trace = FALSE)
summary(step.back.aic)
```

```{r}
#Forward Stepwise Search using AIC (IQ)
step.fwd.aic = step(M2, scope = list(lower = M2, upper = M3), direction = "forward", trace = FALSE)
summary(step.fwd.aic)
```

```{r}
sjPlot::tab_model(
step.fwd.aic, step.back.aic,
show.ci = FALSE,
show.aic = TRUE,
dv.labels = c("Forward model (IQ)","Backward model (IQ)")
)
```


```{r}
#5-Fold Cross Validation - Full Model (SJ)
cv_full_sj = train(
  total_cases ~ ., data=sj,
  method = "lm",
  trControl = trainControl(
    method = "cv", number = 5,
    verboseIter = FALSE
  )
)
cv_full_sj
```

```{r}
#5-Fold Cross Validation - Subset Model (SJ)
cv_subset_sj = train(
  total_cases ~ ndvi_se + ndvi_sw + reanalysis_air_temp_k + 
    reanalysis_tdtr_k + station_avg_temp_c + station_max_temp_c, data=sj,
  method = "lm",
  trControl = trainControl(
    method = "cv", number = 5,
    verboseIter = FALSE
  )
)
cv_subset_sj
```

```{r}
#5-Fold Cross Validation - Full Model (IQ)
cv_full_iq = train(
  total_cases ~ ., data=iq,
  method = "lm",
  trControl = trainControl(
    method = "cv", number = 5,
    verboseIter = FALSE
  )
)
cv_full_iq
```

```{r}
#5-Fold Cross Validation - Subset Model (IQ)
cv_subset_iq = train(
  total_cases ~ ndvi_se + ndvi_sw + reanalysis_air_temp_k + 
    reanalysis_tdtr_k + station_avg_temp_c, data=iq,
  method = "lm",
  trControl = trainControl(
    method = "cv", number = 5,
    verboseIter = FALSE
  )
)
cv_subset_iq
```

```{r}
cv_sj = rbind("Full Model (SJ)" = cv_full_sj$results, "Subset Model (SJ)" = cv_subset_sj$results)
cv_sj
```

```{r}
cv_iq = rbind("Full Model (IQ)" = cv_full_iq$results, "Subset Model (IQ)" = cv_subset_iq$results)
cv_iq
```

```{r}
rmse_sj_full = 49.19337**2
rmse_sj_ss = 48.55353**2
mse_sj = rbind("Full Model (SJ)" = rmse_sj_full, "Subset Model (SJ)" = rmse_sj_ss)
colnames(mse_sj) <- c("MSE")

mse_sj
```

```{r}
rmse_iq_full = 11.35435**2
rmse_iq_ss = 10.67549**2
mse_iq = rbind("Full Model (IQ)" = rmse_iq_full, "Subset Model (IQ)" = rmse_iq_ss)
colnames(mse_iq) <- c("MSE")

mse_iq
```

```{r}

```